---
title: "Canonical Correlation Analysis"
output: html_document  
always_allow_html: true
---


```{r setup,echo=FALSE,results='hide', include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(GGally)
library(CCA)
library(CCP)
library(Hmisc)
library(dplyr)
library(knitr)
library(kableExtra)
```
## RESULT
Canonical Correlation Analysis  

```{r, echo = FALSE}
csvfile <- reactive({
  csvfile <- input$file1
  if (is.null(csvfile)) {
    return(NULL)
  }
  dt <- read.csv(csvfile$datapath, header = input$header, sep = ",")
  dt
})
################################ Correlation Matrix
if (input$submit > 0) {
  x <- csvfile()
  cormat <- Hmisc::rcorr(as.matrix(x))
  R <- round(cormat$r, 3)
  p <- cormat$P
  ## Define notions for significance levels; spacing is important.
  mystars <- ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    ")))
  Rnew <- matrix(paste(R, mystars, sep = ""), ncol = ncol(x))
  diag(Rnew) <- paste(diag(R), " ", sep = "")
  row.names(Rnew) <- names(x)
  colnames(Rnew) <- names(x)
  kable(Rnew, digits = 3, caption = "Pearson correlation between variables", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}  

########################### TEXT under corr matrix
if (input$submit > 0) {
  cat("Significance Indicator: ***0.1%; **1%; *5% level")
}  

######################### Wilks lambda

if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- dim(X)[1]
  p <- length(X)
  q <- length(Y)
  wilk <- as.data.frame(CCP::p.asym(rho, n, p, q, tstat = "Wilks"))
  wilk <- wilk[, -1]
  kable(wilk, digits = 3, caption = "Wilks' Lambda, using F-approximation (Rao's F)", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End wilks

######################### CCA
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  rho_2 <- rho^2
  cancorr <- as.data.frame(cbind(rho, rho_2))
  colnames(cancorr) <- c(
    "Canonical Correlations",
    "Squared Canonical Correlations"
  )
  kable(cancorr, digits = 3, caption = "Canonical Correlation Analysis", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End CCA  

######################### Raw canonical X
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- length(rho)
  raw <- cc1[3:4]
  raw1 <- raw$xcoef
  raw1 <- as.data.frame(raw1)
  colnames(raw1) <- paste("U", 1:n, sep = "")
  raw1
  kable(raw1, digits = 3, caption = "Raw Canonical Coefficients for the set X Variables", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Raw canonical X


######################### Raw canonical Y
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- length(rho)
  raw <- cc1[3:4]
  raw2 <- raw$ycoef
  raw2 <- as.data.frame(raw2)
  colnames(raw2) <- paste("V", 1:n, sep = "")
  raw2
  kable(raw2, digits = 3, caption = "Raw Canonical Coefficients for the set Y Variables", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Raw canonical Y

######################### Correlations Between X Variables and U
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- length(rho)
  cc2 <- CCA::comput(X, Y, cc1)
  load1 <- cc2$corr.X.xscores
  load1 <- as.data.frame(load1)
  colnames(load1) <- paste("U", 1:n, sep = "")
  load1
  kable(load1, digits = 3, caption = "Correlations Between X Variables and their Canonical Variables(U) (Loadings)", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Correlations Between X Variables and U

######################### Correlations Between Y Variables and V
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- length(rho)
  cc2 <- CCA::comput(X, Y, cc1)
  load2 <- cc2$corr.Y.yscores
  load2 <- as.data.frame(load2)
  colnames(load2) <- paste("V", 1:n, sep = "")
  load2
  kable(load2, digits = 3, caption = "Correlations Between Y Variables and their Canonical Variables(V) (Loadings)", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Correlations Between Y Variables and V


######################### Correlation between X variables and V
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
  Y <- as.data.frame(subset(csvfile(), select = input$Y))
  cc1 <- CCA::cc(X, Y)
  rho <- cc1$cor
  n <- length(rho)
  cc2 <- CCA::comput(X, Y, cc1)
  load3 <- cc2$corr.X.yscores
  load3 <- as.data.frame(load3)
  colnames(load3) <- paste("V", 1:n, sep = "")
  load3
  kable(load3, digits = 3, caption = "Correlations Between X Variables and the opposite group of canonical variates (V) (Loadings)", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Correlations Between X Variables and V

######################### Correlation between Y variables and U
if (input$submit > 0) {
  X <- as.data.frame(subset(csvfile(), select = input$X))
        Y <- as.data.frame(subset(csvfile(), select = input$Y))
        cc1 <- CCA::cc(X, Y)
        rho <- cc1$cor
        n <- length(rho)
        cc2 <- CCA::comput(X, Y, cc1)
        load4 <- cc2$corr.Y.xscores
        load4 <- as.data.frame(load4)
        colnames(load4) <- paste("U", 1:n, sep = "")
        load4
  kable(load4, digits = 3, caption = "Correlations Between Y Variables and the opposite group of canonical variates (U) (Loadings)", align = "c", row.names = TRUE) %>%
    kable_styling(bootstrap_options = c("hover"))
}
######################## End Correlations Between Y Variables and  
tags$br()
tags$br()
tags$br()
tags$br()
```  



### report generated from:  

**grapesCancor**


**Developed by:**

Dr.Pratheesh P. Gopinath

Asst. Professor

Agricultural Statistics

Kerala Agricultural University

**&**

Sandra M.M.

M.Sc.(Agricultural Statistics)

College of Agriculture Vellayani  


::: {#hello .greeting .message style="color: #c9c6c5;"}  
<center>  

**You can copy the results table to MS Word. If the table is large use Layout Orientation landscape in Word**  

</center>
:::  

## .  

## .
